### 2023-10-09 main.tex
fix

\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by 

@@

\paragraph{One point correlations}

@@

\paragraph{Two points correlations}
The two points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 

@@

The three points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$

>>>>

\paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by 

@@

\paragraph{One-point correlations}

@@

\paragraph{Two-point correlations}
The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 

@@

The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
